### 2022-01-26 input/background.tex
complete pass on background + comment

Figure~\ref{fig:partition_intuition} depicts an infrastructure
comprising 17 interconnected \processes spread across France. In
Figure~\ref{fig:partition_intuitionA}, a single \Process~$R$ hosts the
content, so every other \process downloads from this \process when it
needs it. In that regard, \Process~$R$ only needs to disseminate a
message notifying all other \processes of its new
content. \Process~$R$ can use uniform reliable
broadcast~\cite{hadzilacos1994modular} and epidemic
propagation~\cite{epidemic-protocol} to guarantee that
\begin{inparaenum}[(i)]
\item every \process eventually knows the content location
\item by efficiently using neighbor-to-neighbor communication.
\end{inparaenum}
\textcolor{red}{Je ne vois pas l'interet des enums ici? ca casse la lecture}
\item [Location:]

@@

Then, in Figure~\ref{fig:partition_intuitionC}, another \Process~$B$
creates a replica of this content. Similarly to \Process~$R$ and
\Process~$G$, \Process~$B$ can notify other \processes of this new
replica. However, the set of \processes that could actually use this
new replica is actually much smaller than the network size. Uniform
reliable broadcast is not designed for such a context and would
generate a lot of unnecessary traffic. Instead, \processes need a
communication primitive that propagates notifications within a scope
by evaluating a predicate, starting at its broadcaster (the
\emph{source}).  In other terms, \processes propagate notifications as
long as they consider them useful based on location information they
carry. We call such a primitive \emph{scoped broadcast} (see
Section~\ref{subsec:scoped}), for messages transitively reach a subset
of interconnected \processes (the \emph{scope}). Using this primitive,
\processes can lock down the traffic of content indexing to relevant
\processes.

@@

Every \process ends up with at least one known replica that is its
closest. The set of interconnected \processes with the same closest
replica is a \emph{partition}. Every \process belongs to one, and only
one, partition (see Section~\ref{subsec:consistent}).

@@

In Figure~\ref{fig:partition_intuitionD}, \Process $G$ destroys its
replica. Every \process that belonged to its green partition must
choose another partition to be in. While it makes sense for
\Process~$G$ to scoped broadcast its removal, \Process~$B$ and
\Process~$R$ cannot afford to continuously advertise their replica to
fill the gap left open by \Process~$G$. Instead, we want to trigger
once again scoped broadcast at bordering \processes of red and blue
partitions. The scope of scoped broadcast changes over receipts by
\processes. Dynamic partitioning raises additional challenges related
to concurrent operations where removed partitions would block the
propagation of other partitions (see Section~\ref{subsec:dynamic}).

@@

Next Section details the properties of scoped broadcast and dynamic
partitioning in dynamic networks, and provides an implementation
called \NAME along with its complexity.

>>>>

Figure~\ref{fig:partition_intuition} depicts an infrastructure
comprising 17 interconnected \processes spread across France. In
Figure~\ref{fig:partition_intuitionA}, a single \Process~$R$ hosts the
content, so every other \process downloads from this \process when it
needs it. In that regard, \Process~$R$ only needs to disseminate a
message notifying all other \processes of its new
content. \Process~$R$ can use uniform reliable
broadcast~\cite{hadzilacos1994modular} and epidemic
propagation~\cite{epidemic-protocol} to guarantee that
\begin{inparaenum}[(i)]
\item every \process eventually knows the content location
\item by efficiently using neighbor-to-neighbor communication.
\end{inparaenum}
\note{Je ne vois pas l'interet des enums ici? ca casse la lecture}
\item [Location:]

@@

Then, in Figure~\ref{fig:partition_intuitionC}, another \Process~$B$
creates a replica of this content. Similarly to \Process~$R$ and
\Process~$G$, \Process~$B$ can notify other \processes of this new
replica. However, the set of \processes that could actually use this
new replica is actually much smaller than the network size. Uniform
reliable broadcast is not designed for such a context and would
generate a lot of unnecessary traffic. Instead, \processes need a
communication primitive that propagates notifications within a scope
by evaluating a predicate, starting at its broadcaster (the
\emph{source}).  In other terms, \processes propagate notifications as
long as they consider them useful based on location information they
carry. We call such a primitive \emph{scoped broadcast}
\note{connerie: ca marche pas comme ca la propagation des routes dans les routeurs?On est pas entrain de reinventer une algo qui existe depuis bien longtemps dans la communauté reseau? Si ce n'est pas le cas alors nous avons une autre application pour as-cast}
(see
Section~\ref{subsec:scoped}), for messages transitively reach a subset
of interconnected \processes (the \emph{scope}). Using this primitive,
\processes can lock down the traffic of content indexing to relevant
\processes.

@@

Every \process ends up with at least one known replica that is its
closest. The set of interconnected \processes with the same closest
replica is a \emph{partition}. Every \process belongs to one, and only
one, partition (see Section~\ref{subsec:consistent}).
In Figure~\ref{fig:partition_intuitionC}, there are three logical partitions.

@@

In Figure~\ref{fig:partition_intuitionD}, \Process $G$ destroys its
replica. Every \process that belonged to its green partition must
choose another partition to be in. While it makes sense for
\Process~$G$ to scoped broadcast its removal, \Process~$B$ and
\Process~$R$ cannot afford to continuously advertise their replica to
fill the gap left open by \Process~$G$. A better approach would
consist in triggering scoped broadcast at bordering \processes of red
and blue partitions once again. In other words, the scope of scoped broadcast changes
over receipts by \processes. This dynamic partitioning raises additional
challenges related to concurrent operations where removed partitions
would\note{can?} block the propagation of other partitions (see
Section~\ref{subsec:dynamic}).

@@

Next Section details the properties of scoped broadcast and dynamic
partitioning, % in dynamic networks,
and provides an implementation called \NAME.% along with its complexity.
